### 2014-11-13 tex/bisimulation.tex
updated the proofs

\section{Bisimilarity Relation}
\label{sec:bisim}
Recall that $p \rgse p^\prime$ is the binary relation over the universe of states, $S$,
according to GSE with lazy initialization. Similarly, $q \rsym q^\prime$ is the relation for the summary heap algorithm
presented in this paper. The principle theoretical result is the
existence of a bisimulation between states related on $p \rgse p^\prime$
and the states related on $q \rsym q^\prime$.  A corollary is that $\rsym$ is
both sound and complete with respect to properties provable in $\rgse$. Only a summary of the
proofs is given due to space.

@@

The proof only reasons about well-formed states: heaps are
deterministic, type consistent, with no dangling references, and it
knows about any references in the environment, expression, or
continuation. Well-formed states always have a successor unless it is
the end of the program execution. It is trivial to show that every
rule in the transition relation preserves well-formedness.

Let $p \rgse p^\prime$ be defined as a union over state relations:
$$
\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom
$$
where \emph{A} is a field access after evaluating the expression for the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write after evaluating the expression for the right operand$\lp
\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the left and right operand expressions $\lp
\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, the prime symbol
indicates a null reference in the operation or a false outcome, and
\emph{\com} is everything else in the language. Any state relation, say $\rightarrow_x$, is trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The definition embodies the notion of splitting groups of heaps at
certain operations. The set $P$ at a field access after base reference is known, for example, has two
potential successors: a non-null and null reference. The $\rsgse$ relation has two successors at that point to divide $P$ into the two outcomes. In contrast, the
set $P \rgse^\com P^\prime$ only has a single successor since anything in $\rightarrow_\com$ is not related to control flow (e.g., variable look up, creating continuations, etc.).

>>>>

\section{Bisimilarity Proof}
\label{sec:bisim}
Recall that $p \rgse p^\prime$ is the binary relation over the universe of states, $S$,
according to GSE with lazy initialization. Similarly, $q \rsym q^\prime$ is the relation for the summary heap algorithm
presented in this paper. The principle theoretical result is the
existence of a bisimulation between states related on $p \rgse p^\prime$
and the states related on $q \rsym q^\prime$.  A corollary is that $\rsym$ is
both sound and complete with respect to properties provable in $\rgse$. Only a summary of the
proofs is given due to space.

@@

The proof only reasons about well-formed states, which have
deterministic, type-consistent heaps, and feasible environments, expressions, and
continuations. Well-formed states always have successors unless at the end of a 
program execution. It is trivial to show that the set of well-formed states is closed
under the transition relation.

Let $p \rgse p^\prime$ be defined as a union over state relations:
$$
\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom
$$
where \emph{A} is a field access after evaluating the expression for the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write after evaluating the expression for the right operand$\lp
\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the left and right operand expressions $\lp
\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, the prime symbol
indicates a null reference in the operation or a false outcome, and
\emph{\com} is everything else in the language. Any state relation, say $\rightarrow_x$, is trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
This definition embodies the notion of splitting groups of heaps at
certain operations. For example, suppose we have a set $P$ containing a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors: one with a non-null reference, and one with a null reference. 
The $\rsgse$ relation has two successors at that point to divide $P$ into the two outcomes. In contrast, the
set $P \rgse^\com P^\prime$ only has a single successor since anything in $\rightarrow_\com$ is not related to control flow (e.g., variable look up, creating continuations, etc.).

### 2014-11-13 tex/proofs.tex
Reworked supplemental upto definitions and proofs.
updated the proofs

\section{Proofs}

\input{definitions}

\subsection{Theorems}

@@

\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
\label{lem:init}
If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
 $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
\end{lemma}

@@

%proof for field write
\begin{lemma}[Exactness of Field Write Rule]
\label{lem:write}
If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
\begin{equation}
\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}
and
\begin{equation}
\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}
\end{lemma}
\begin{proof}
Begin by assuming the conditions from Lemma~\ref{lem:write}.

@@

\begin{lemma}[$\rsum^*$ produces well-formed heaps]
\label{lem:S-determ}
Given a deterministic heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the 
summary machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
\rsum^*
(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, is also deterministic.
\end{lemma}
\begin{proof}
Induction over the number of steps in $\rsum^*$ in \figref{fig:symInit}.

@@

\begin{lemma}[$\rightarrow_\mathit{FA}$ produces well-formed heaps]
\label{lem:FA-determ}
Given a state, $s$, with a deterministic heap,
$(\cfgnt{L}\ \cfgnt{R}) =
\mathrm{heap}(s)$, the new heap,
$(\cfgnt{L}^\prime\ \cfgnt{R}^\prime) =
\mathrm{heap}(s^\prime)$, in any state related by the field
access rule, $s \rightarrow_\mathit{FA} s^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FA}$ in \figref{fig:sym}.

@@

\begin{lemma}[$\rightarrow_\mathit{FW}$ produces well-formed heaps]
\label{lem:FW-determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the field
write rule, $s_\sym \rightarrow_\mathit{FW} s_\sym^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:sym}.

@@

\begin{lemma}[$\rcom$ produces well-formed heaps]
\label{lem:J-determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the
Javalite relation, $s_\sym \rcom s_\sym^\prime$, is
also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rcom$ in \figref{fig:javalite-common}.

@@

\begin{lemma}[Exactness of Reference Compare Rule]
\label{lem:compare}
If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
\begin{equation}
\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}
and
\begin{equation}
\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}
\end{lemma}
There are two rules that apply to state $s_\sym$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch. Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch. 
\begin{proof}
Assume there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$. Let $s_\sym^\prime$ be any state such that $s_\sym \rsym s_\sym$ and let $\zeta_T = \forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime )$. Since $s_\gse \sqsubset s_\sym$, we know that $s_\gse \in \mathcal{RC}$, and that there exists a homomorphism $s_\gse \rightharpoonup_{h} s_\sym$ such that $\mathbb{S}( \phi_\sym \wedge \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym) ) $. We partition $\zeta_T$ based on the values of $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$ as follows: Let
$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\gse\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
and let
$$\zeta_f = \zeta_T \setminus \zeta_t$$

@@

\begin{lemma}[Exactness of New Rule]
\label{lem:new}
If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{NW}$ and $s_\gse \sqsubset s_\sym$, then:
\begin{equation}
\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}
and
\begin{equation}
\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}

\begin{proof}
The proof is left as an exercise to the reader.
\end{proof}

\end{lemma}

>>>>

\section{Proofs}
\subsection{Lemmas}

@@

\begin{theorem}
If $R \subseteq F\sim(R)$, then $R$ is a bisimulation.
\label{lem:bisim}
\end{theorem}
The proof can be found in any good text on bisimulation.
%For the proof, we refer the reader to \cite{Sangiorgi:2011}

\begin{theorem}

\end{theorem}

%\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
%\label{lem:init}
%If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
% $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
%\end{lemma}

\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
\label{lem:init}
If $P \sqsubset q$ and if $\exists q^\prime (q \rsym q^\prime )$ , then $\exists 
\end{lemma}

@@

%proof for field write
%\begin{lemma}[Exactness of Field Write Rule]
%\label{lem:write}
%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
%\begin{equation}
%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%\end{lemma}

\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{W{\footnotesize RITE}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{FW}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{FW}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

\begin{proof}
Begin by assuming the conditions from Lemma~\ref{lem:write}.

@@

\begin{lemma}[$\rsum^*$ preserves heap determinism]
\label{lem:S-determ}
Given a deterministic heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the 
summary machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
\rsum^*
(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, is also deterministic.
\end{lemma}
\begin{proof}
Induction over the number of steps in $\rsum^*$ in \figref{fig:symInit}.

@@

\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves heap determinism]
\label{lem:FA-determ}
Given a state, $s$, with a deterministic heap,
$(\cfgnt{L}\ \cfgnt{R}) =
\mathrm{heap}(s)$, the new heap,
$(\cfgnt{L}^\prime\ \cfgnt{R}^\prime) =
\mathrm{heap}(s^\prime)$, in any state related by the field
access rule, $s \rightarrow_\mathit{FA} s^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FA}$ in \figref{fig:sym}.

@@

\begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
\label{lem:FW-determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the field
write rule, $s_\sym \rightarrow_\mathit{FW} s_\sym^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:sym}.

@@

\begin{lemma}[$\rcom$ preserves heap determinism]
\label{lem:J-determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the
Javalite relation, $s_\sym \rcom s_\sym^\prime$, is
also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rcom$ in \figref{fig:javalite-common}.

@@

%\begin{lemma}[Exactness of Reference Compare Rule]
%\label{lem:compare}
%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
%\begin{equation}
%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%\end{lemma}

\begin{lemma}[\textrm{E{\footnotesize QUALS}} } preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{E}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{E}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

There are two rules that apply to state $s_\sym \in 2^{E}$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch. Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch. 
\begin{proof}
Assume there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$. Let $s_\sym^\prime$ be any state such that $s_\sym \rsym s_\sym$ and let $\zeta_T = \forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime )$. Since $s_\gse \sqsubset s_\sym$, we know that $s_\gse \in \mathcal{RC}$, and that there exists a homomorphism $s_\gse \rightharpoonup_{h} s_\sym$ such that $\mathbb{S}( \phi_\sym \wedge \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym) ) $. We partition $\zeta_T$ based on the values of $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$ as follows: Let
$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\gse\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
and let
$$\zeta_f = \zeta_T \setminus \zeta_t$$

@@

%\begin{lemma}[Exactness of New Rule]
%\label{lem:new}
%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{NW}$ and $s_\gse \sqsubset s_\sym$, then:
%\begin{equation}
%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}

%\end{lemma}

%
%\begin{proof}
%The proof follows immediately from the rule.
%\end{proof}
